---
title: "Take_Home_Exercise_1"
author: "WEN Po-Yang"
date: last-modified
date-format: "YYYY-MM-DD HH:mm"
format:
  html:
    css: styles_the4.css
---

# 1.Overview

This take-home exercise transforms raw survey responses into decision-relevant insights using visually-driven survey analysis. The dataset contains demographic/background variables (e.g., study year, gender, parental education) and multiple Likert-scale items describing perceived learning conditions and support.

Following the requirements, the analysis workflow is fully reproducible using tidyverse for data processing and ggplot2 (and extensions) for visualisation. The final deliverable presents 5–10 key observations supported by clear graphics, with each visualisation accompanied by a short interpretation (≤150 words).

# 2.Data Preparation

## 2.1 Load Packages

```{r}
#| warning: false
pacman::p_load(
  tidyverse,
  readxl,
  janitor,
  scales,
  waffle
)
```

## 2.2 Import Data

```{r}
raw <- read_excel("data/Database paper.xlsx") %>%
  clean_names()

glimpse(raw)
```

## 2.3 Basic Data Checks (Structure, Missingness, Duplicate Rows)

::: panel-tabset
## Data Dimensions

```{r}
# Dimensions
dim(raw)
```

## Missing Values

```{r}
# Quick missingness profile
raw %>%
  summarise(across(everything(), ~sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") %>%
  arrange(desc(n_missing)) %>%
  print(n = 50)
```

## Duplicate Rows

```{r}
# Check duplicated rows (if any)
raw %>% duplicated() %>% sum()
```
:::

## 2.4 Recode Variables Using The Codebook

In the raw dataset, categorical responses are stored as numeric codes. To ensure interpretability and correct ordering in plots, variables are recoded into factors (ordered where appropriate). This step aligns the data structure with survey analysis best practices and ensures that ggplot2 displays categories in meaningful order.

::: panel-tabset
## Recoding and Labeling Survey Variables (Code Chunk 1)

```{r}
likert_5 <- c("Not at all", "Little", "Moderate", "Quite", "Very")

survey <- raw |>
  mutate(
    # A.1 Year
    year = factor(
      year,
      levels = 1:5,
      labels = c("First-year", "Second-year", "Third-year", "Fourth-year", "Graduated"),
      ordered = TRUE
    ),

    # A.2 Gender
    gender = factor(gender, levels = c(1, 2), labels = c("Male", "Female")),

    # A.3–A.5 Yes/No
    policy_stu   = factor(policy_stu,   levels = c(1, 2), labels = c("Yes", "No")),
    minority_stu = factor(minority_stu, levels = c(1, 2), labels = c("Yes", "No")),
    poor_stu     = factor(poor_stu,     levels = c(1, 2), labels = c("Yes", "No")),

    # A.6–A.7 Parental education
    father_edu = factor(
      father_edu,
      levels = 1:6,
      labels = c("Primary", "Secondary", "High school", "College",
                 "University/Graduate", "Other"),
      ordered = TRUE
    ),
    mother_edu = factor(
      mother_edu,
      levels = 1:6,
      labels = c("Primary", "Secondary", "High school", "College",
                 "University/Graduate", "Other"),
      ordered = TRUE
    ),

    # A.8–A.9 Parental occupation
    father_occupation = factor(
      father_occupation,
      levels = 1:5,
      labels = c("Government employee", "Self-employment", "Freelance", "Other", "Not public")
    ),
    mother_occupation = factor(
      mother_occupation,
      levels = 1:5,
      labels = c("Government employee", "Self-employment", "Freelance", "Other", "Not public")
    ),

    # A.10–A.12 Time use (ordered)  
    time_friends = factor(
      time_friends,
      levels = 1:5,
      labels = c("Under 1 hour", "1–<2 hours", "2–<3 hours", "3–<4 hours", "Over 4 hours"),
      ordered = TRUE
    ),
    time_socical_media = factor(
      time_socical_media,
      levels = 1:5,
      labels = c("Under 1 hour", "1–<2 hours", "2–<3 hours", "3–<4 hours", "Over 4 hours"),
      ordered = TRUE
    ),
    time_studying = factor(
      time_studying,
      levels = 1:5,
      labels = c("Under 2 hours", "2–<4 hours", "4–<6 hours", "6–<8 hours", "Over 8 hours"),
      ordered = TRUE
    ),

    # A.13 GPA (ordered) + numeric version for correlation/mean plots (Obs 5 & 7)
    gpa = factor(
      gpa,
      levels = 1:5,
      labels = c(
        "Under 2.0 (Poor)",
        "2.0–<2.5 (Average)",
        "2.5–<3.2 (Fair)",
        "3.2–<3.6 (Good)",
        "Over 3.6 (Excellent)"
      ),
      ordered = TRUE
    ),
    gpa_num = as.integer(gpa),  # 1..5 (good for Spearman / trend)

    # B items (Likert; ordered) 
    adapt_learning_uni   = factor(adapt_learning_uni,   levels = 1:5, labels = likert_5, ordered = TRUE),
    study_methods        = factor(study_methods,        levels = 1:5, labels = likert_5, ordered = TRUE),
    support_of_uni       = factor(support_of_uni,       levels = 1:5, labels = likert_5, ordered = TRUE),
    support_of_lec       = factor(support_of_lec,       levels = 1:5, labels = likert_5, ordered = TRUE),
    facilitie_uni        = factor(facilitie_uni,        levels = 1:5, labels = likert_5, ordered = TRUE),
    quality_lecturer     = factor(quality_lecturer,     levels = 1:5, labels = likert_5, ordered = TRUE),
    training_curriculum  = factor(training_curriculum,  levels = 1:5, labels = likert_5, ordered = TRUE),
    competitive_class    = factor(competitive_class,    levels = 1:5, labels = likert_5, ordered = TRUE),
    infuence_f_friends   = factor(infuence_f_friends,   levels = 1:5, labels = likert_5, ordered = TRUE)
  )

```

## Likert Data to Long Format (Code Chunk 2)

```{r}
likert_long <- survey |>
  dplyr::select(
    year, gender, gpa, gpa_num,
    adapt_learning_uni, study_methods,
    support_of_uni, support_of_lec,
    facilitie_uni, quality_lecturer,
    training_curriculum, competitive_class,
    infuence_f_friends
  ) |>
  tidyr::pivot_longer(
    cols = c(
      adapt_learning_uni, study_methods,
      support_of_uni, support_of_lec,
      facilitie_uni, quality_lecturer,
      training_curriculum, competitive_class,
      infuence_f_friends
    ),
    names_to = "item",
    values_to = "response"
  ) |>
  dplyr::mutate(
    response_num = as.integer(response),
    item = dplyr::recode(item,
      adapt_learning_uni  = "Adapt to learning environment",
      study_methods       = "Study methods",
      support_of_uni      = "University support",
      support_of_lec      = "Lecturer support",
      facilitie_uni       = "University facilities",
      quality_lecturer    = "Lecturer quality",
      training_curriculum = "Curriculum suitability",
      competitive_class   = "Class competition effect",
      infuence_f_friends  = "Friends' influence"
    )
  )

```
:::

# 3.Observations

## Observation1 - Sample profiles shows strong imbalance (Year and Gender)

The respondent pool is not evenly distributed across key demographics. Graduated students constitute a noticeably large share of the sample, while earlier cohorts represent a smaller proportion. In addition, female respondents dominate the dataset. This matters because subsequent “overall” patterns (e.g., average perceptions or GPA distribution) will largely reflect the experience of the majority groups rather than the entire student population. Therefore, the findings should be interpreted as describing this specific respondent composition, and comparisons across groups (where sample sizes differ substantially) should be treated cautiously. Establishing this sample profile upfront helps contextualize later observations and reduces the risk of over-generalizing from an imbalanced survey sample.

::: panel-tabset
## The Plot

```{r}
#| echo: false
year_tbl <- survey |> count(year) |> mutate(pct = n/sum(n))
gender_tbl <- survey |> count(gender) |> mutate(pct = n/sum(n))


library(patchwork)
library(ggthemes)

p1 <- year_tbl |>
  ggplot(aes(x = year, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Study year", x = NULL, y = "Share") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

p2 <- gender_tbl |>
  ggplot(aes(x = gender, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Gender", x = NULL, y = "Share") +
  theme_minimal()

p1 + p2 + plot_annotation(title = "Respondent Profile")

```

## The Code Chunk

```{r}
#| eval: false
year_tbl <- survey |> count(year) |> mutate(pct = n/sum(n))
gender_tbl <- survey |> count(gender) |> mutate(pct = n/sum(n))


library(patchwork)
library(ggthemes)

p1 <- year_tbl |>
  ggplot(aes(x = year, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Study year", x = NULL, y = "Share") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))

p2 <- gender_tbl |>
  ggplot(aes(x = gender, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(title = "Gender", x = NULL, y = "Share") +
  theme_minimal()

p1 + p2 + plot_annotation(title = "Respondent Profile")

```
:::

## Observation 2 — GPA distribution is middle-heavy (Fair/Good dominate)

GPA responses cluster strongly in the middle categories, with “Fair” and “Good” making up most of the sample. Both tails—“Poor” and “Excellent”—are relatively small. This middle-heavy distribution suggests that most respondents report moderate academic performance rather than extreme outcomes. As a result, later comparisons (e.g., GPA by study behaviors) are more likely to reveal incremental shifts rather than sharp separations. It also implies that visual patterns such as monotonic trends (e.g., increasing/decreasing average GPA across ordered groups) may be more informative than searching for rare high/low outliers. Overall, this distribution provides a stable baseline for interpreting associations between perceived learning conditions and academic performance.

::: panel-tabset
## The Plot

```{r}
#| echo: false
survey |>
  count(gpa) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = gpa, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = NULL, y = "Share of respondents", title = "GPA distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

## The Code Chunk

```{r}
#| eval: false
survey |>
  count(gpa) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = gpa, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = NULL, y = "Share of respondents", title = "GPA distribution") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```
:::

## Observation 3 — Self-reported study time is highly concentrated at “Over 8 hours”

Self-reported study time is heavily concentrated in the highest category (“Over 8 hours”), while lower time brackets account for a comparatively small share of respondents. This creates a potential ceiling effect: when most observations sit at the upper end, the data provides limited contrast for detecting differences in outcomes across study-time groups. Practically, this means study time may appear weakly related to GPA not because it is irrelevant, but because the survey responses are compressed into one dominant category. This pattern may reflect real behavior among respondents, differences in how individuals interpret the time brackets, or response bias (e.g., socially desirable reporting). Recognizing this distributional issue is important before using study time as an explanatory factor in later comparisons.

::: panel-tabset
## The Plot

```{r}
#| echo: false
survey |>
  count(time_studying) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = time_studying, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = NULL, y = "Share of respondents", title = "Daily time spent studying") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

## The Code Chunk

```{r}
#| eval: false
survey |>
  count(time_studying) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = time_studying, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = NULL, y = "Share of respondents", title = "Daily time spent studying") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```
:::

## Observation 4 — Likert items skew positive; “Adaptation” is comparatively lower

Across the nine Likert-scale dimensions, responses generally lean toward the positive end (“Quite” and “Very”), indicating broadly favorable perceptions of learning conditions and support. However, the pattern is not uniform across items. Relative to other dimensions, “Adapt to learning environment” attracts fewer top-end responses and a higher share of mid-range ratings, suggesting that students may feel less confident about their personal adjustment even when they view institutional or lecturer-related factors positively. In contrast, items such as lecturer quality and lecturer support tend to receive stronger top-end agreement, indicating higher perceived strength in teaching-related aspects. This cross-item comparison helps prioritize which areas appear consistently strong versus which may be perceived as comparatively weaker.

::: panel-tabset
## The Plot

```{r}
#| echo: false
likert_dist <- likert_long |>
  count(item, response) |>
  group_by(item) |>
  mutate(pct = n / sum(n)) |>
  ungroup()

likert_dist |>
  ggplot(aes(x = pct, y = fct_reorder(item, pct, .fun = sum), fill = response)) +
  geom_col() +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(x = "Share of responses", y = NULL, title = "Perceptions across learning-related dimensions") +
  theme_minimal()
```

## The Code Chunk

```{r}
#| eval: false
likert_dist <- likert_long |>
  count(item, response) |>
  group_by(item) |>
  mutate(pct = n / sum(n)) |>
  ungroup()

likert_dist |>
  ggplot(aes(x = pct, y = fct_reorder(item, pct, .fun = sum), fill = response)) +
  geom_col() +
  scale_x_continuous(labels = scales::percent_format()) +
  labs(x = "Share of responses", y = NULL, title = "Perceptions across learning-related dimensions") +
  theme_minimal()
```
:::

## Observation 5 — Strongest GPA association appears in “Study methods” and “Adaptation”

Comparing the Likert dimensions by their Spearman correlation with GPA highlights which perceptions align most strongly with academic performance. “Study methods” shows the highest positive association with GPA, suggesting that students who rate their study strategies more favorably also tend to report higher GPA categories. “Adapt to learning environment” is also among the stronger correlates, indicating that better self-reported adjustment is linked to better academic outcomes. Other dimensions, such as facilities or perceived class competition, show weaker associations, implying that they vary less systematically with GPA in this sample. Importantly, these correlations are descriptive and do not establish causality; they indicate which perceived factors co-move with GPA and therefore may be most informative for targeted interpretation and discussion.

```{r}
#| include: false
set.seed(123)

boot_corr <- likert_long |>
  filter(!is.na(gpa_num), !is.na(response_num)) |>
  group_by(item) |>
  summarise(
    # bootstrap 300 resamples
    r_boot = list(replicate(300, {
      idx <- sample.int(n(), replace = TRUE)
      suppressWarnings(cor(response_num[idx], gpa_num[idx], method = "spearman"))
    })),
    .groups = "drop"
  ) |>
  mutate(
    r_med = map_dbl(r_boot, median, na.rm = TRUE),
    r_lo  = map_dbl(r_boot, ~quantile(.x, 0.025, na.rm = TRUE)),
    r_hi  = map_dbl(r_boot, ~quantile(.x, 0.975, na.rm = TRUE))
  ) |>
  select(item, r_med, r_lo, r_hi) |>
  arrange(r_med)
```

::: panel-tabset
## The Plot

```{r}
#| echo: false
#| warning: false
boot_corr |>
  ggplot(aes(x = r_med, y = forcats::fct_reorder(item, r_med))) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = r_lo, xmax = r_hi), height = 0.2) +
  geom_point(size = 2) +
  labs(
    x = "Spearman correlation with GPA (median, 95% bootstrap interval)",
    y = NULL,
    title = "Which perceived dimensions align most with GPA?"
  ) +
  theme_minimal()
```

## The Codoe Chunk

```{r}
#| eval: false
boot_corr |>
  ggplot(aes(x = r_med, y = forcats::fct_reorder(item, r_med))) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_errorbarh(aes(xmin = r_lo, xmax = r_hi), height = 0.2) +
  geom_point(size = 2) +
  labs(
    x = "Spearman correlation with GPA (median, 95% bootstrap interval)",
    y = NULL,
    title = "Which perceived dimensions align most with GPA?"
  ) +
  theme_minimal()
```
:::

### Inferential Statistics: ggbetweenstats()

```{r}
#| message: false
#| warning: false
#| include: false
library(tidyverse)
library(ggstatsplot)
library(ggthemes)

df_gpa2 <- likert_long %>%
  mutate(
    gpa_group = case_when(
      gpa_num <= 3 ~ "Low GPA",
      gpa_num >= 4 ~ "High GPA",
      TRUE ~ NA_character_
    ),
    gpa_group = factor(gpa_group, levels = c("Low GPA", "High GPA"))
  ) %>%
  filter(!is.na(gpa_group), !is.na(response_num))
```

::: panel-tabset
## Plot 1

```{r}
#| echo: false
#| message: false
#| warning: false
df_gpa2 %>%
  filter(item == "Study methods") %>%
  ggstatsplot::ggbetweenstats(
    x = gpa_group,
    y = response_num,
    type = "np",
    pairwise.comparisons = FALSE,
    results.subtitle = FALSE,   
    messages = FALSE,
    xlab = NULL,
    ylab = "Likert score (1–5)",
    title = "Study methods"
  ) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  ggthemes::theme_clean(base_size = 12) +
  theme(legend.position = "none")
```

## The Code Chunk

```{r}
#| eval: false
df_gpa2 %>%
  filter(item == "Study methods") %>%
  ggstatsplot::ggbetweenstats(
    x = gpa_group,
    y = response_num,
    type = "np",
    pairwise.comparisons = FALSE,
    results.subtitle = FALSE,   
    messages = FALSE,
    xlab = NULL,
    ylab = "Likert score (1–5)",
    title = "Study methods"
  ) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  ggthemes::theme_clean(base_size = 12) +
  theme(legend.position = "none")
```
:::

::: panel-tabset
## Plot 2

```{r}
#| echo: false
#| message: false
#| warning: false
df_gpa2 %>%
  filter(item == "Adapt to learning environment") %>%
  ggstatsplot::ggbetweenstats(
    x = gpa_group,
    y = response_num,
    type = "np",
    pairwise.comparisons = FALSE,
    results.subtitle = FALSE,
    messages = FALSE,
    xlab = NULL,
    ylab = "Likert score (1–5)",
    title = "Adapt to learning environment"
  ) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  ggthemes::theme_clean(base_size = 12) +
  theme(legend.position = "none")
```

## The Code Chunk

```{r}
#| eval: false
df_gpa2 %>%
  filter(item == "Adapt to learning environment") %>%
  ggstatsplot::ggbetweenstats(
    x = gpa_group,
    y = response_num,
    type = "np",
    pairwise.comparisons = FALSE,
    results.subtitle = FALSE,
    messages = FALSE,
    xlab = NULL,
    ylab = "Likert score (1–5)",
    title = "Adapt to learning environment"
  ) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  ggthemes::theme_clean(base_size = 12) +
  theme(legend.position = "none")
```
:::

::: panel-tabset
## Plot 3

```{r}
#| echo: false
#| message: false
#| warning: false
df_gpa2 %>%
  filter(item == "University facilities") %>%
  ggstatsplot::ggbetweenstats(
    x = gpa_group,
    y = response_num,
    type = "np",
    pairwise.comparisons = FALSE,
    results.subtitle = FALSE,
    messages = FALSE,
    xlab = NULL,
    ylab = "Likert score (1–5)",
    title = "University facilities"
  ) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  ggthemes::theme_clean(base_size = 12) +
  theme(legend.position = "none")
```

## The Code Chunk

```{r}
#| eval: false
df_gpa2 %>%
  filter(item == "University facilities") %>%
  ggstatsplot::ggbetweenstats(
    x = gpa_group,
    y = response_num,
    type = "np",
    pairwise.comparisons = FALSE,
    results.subtitle = FALSE,
    messages = FALSE,
    xlab = NULL,
    ylab = "Likert score (1–5)",
    title = "University facilities"
  ) +
  scale_y_continuous(breaks = 1:5, limits = c(1, 5)) +
  ggthemes::theme_clean(base_size = 12) +
  theme(legend.position = "none")
```
:::

## Observation 6 — Friends’ influence is rated non-trivially, yet shows little GPA differentiation

Responses indicate that peers are perceived to have a meaningful influence, with many respondents selecting mid-to-high agreement levels rather than “Not at all.” Despite this perception, GPA patterns across friends’ influence categories show little separation: the mean GPA category remains fairly stable, and confidence intervals overlap substantially across groups. This suggests a disconnect between perceived peer influence and reported academic outcomes in this dataset. One possible interpretation is that friends affect aspects of student life not directly captured by GPA, or that positive and negative peer effects offset each other in aggregate. Alternatively, the influence may be real but not detectable given measurement limitations (ordinal categories and self-report). Either way, this contrast is a useful reminder that perceived importance does not necessarily translate into observable outcome differences.

::: panel-tabset
## Plot 1 (Friends Influence)

```{r}
#| echo: false
# (A) Distribution
p_friends_dist <- survey |>
  count(infuence_f_friends) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = infuence_f_friends, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = NULL, y = "Share of respondents", title = "Friends' influence (distribution)") +
  theme_minimal()

# (B) GPA by friends influence (mean GPA category)
p_friends_gpa <- survey |>
  filter(!is.na(infuence_f_friends), !is.na(gpa_num)) |>
  group_by(infuence_f_friends) |>
  summarise(
    mean_gpa = mean(gpa_num),
    se = sd(gpa_num) / sqrt(n()),
    .groups = "drop"
  ) |>
  ggplot(aes(x = infuence_f_friends, y = mean_gpa)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_gpa - 1.96 * se, ymax = mean_gpa + 1.96 * se), width = 0.1) +
  scale_y_continuous(breaks = 1:5) +
  labs(x = NULL, y = "Mean GPA category (1=Poor … 5=Excellent)",
       title = "GPA by perceived friends' influence") +
  theme_minimal()

p_friends_dist
```

## Plot 2 (GPA By Perceived Friends Influence)

```{r}
#| echo: false
p_friends_gpa
```

## The Code Chunk

```{r}
#| eval: false
# (A) Distribution
p_friends_dist <- survey |>
  count(infuence_f_friends) |>
  mutate(pct = n / sum(n)) |>
  ggplot(aes(x = infuence_f_friends, y = pct)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = NULL, y = "Share of respondents", title = "Friends' influence (distribution)") +
  theme_minimal()

# (B) GPA by friends influence (mean GPA category)
p_friends_gpa <- survey |>
  filter(!is.na(infuence_f_friends), !is.na(gpa_num)) |>
  group_by(infuence_f_friends) |>
  summarise(
    mean_gpa = mean(gpa_num),
    se = sd(gpa_num) / sqrt(n()),
    .groups = "drop"
  ) |>
  ggplot(aes(x = infuence_f_friends, y = mean_gpa)) +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_gpa - 1.96 * se, ymax = mean_gpa + 1.96 * se), width = 0.1) +
  scale_y_continuous(breaks = 1:5) +
  labs(x = NULL, y = "Mean GPA category (1=Poor … 5=Excellent)",
       title = "GPA by perceived friends' influence") +
  theme_minimal()

p_friends_dist
p_friends_gpa
```
:::

## Observation 7 — Heavy social media use shows a negative GPA trend

GPA shows a downward trend as reported time spent on social media increases. Respondents in the lowest usage groups tend to have slightly higher mean GPA categories, while the “Over 4 hours” group exhibits the lowest mean GPA. Although the differences are not necessarily large, the monotonic pattern suggests a consistent association between heavier social media use and weaker academic performance in this sample. This observation should not be interpreted causally: higher social media use may reflect underlying factors such as time management challenges, stress coping behaviors, or differences in study routines. Nevertheless, because the predictor is behavioral and ordered, the visual trend is informative and complements the perception-based findings, offering a practical angle for discussion about student habits and academic outcomes.

::: panel-tabset
## The Plot

```{r}
#| echo: false
survey |>
  filter(!is.na(time_socical_media), !is.na(gpa_num)) |>
  group_by(time_socical_media) |>
  summarise(
    mean_gpa = mean(gpa_num),
    se = sd(gpa_num) / sqrt(n()),
    .groups = "drop"
  ) |>
  ggplot(aes(x = time_socical_media, y = mean_gpa, group = 1)) +
  geom_line() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_gpa - 1.96 * se, ymax = mean_gpa + 1.96 * se), width = 0.1) +
  scale_y_continuous(breaks = 1:5) +
  labs(x = NULL, y = "Mean GPA category (1=Poor … 5=Excellent)",
       title = "GPA trend by time spent on social media") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```

## The Code Chunk

```{r}
#| eval: false
survey |>
  filter(!is.na(time_socical_media), !is.na(gpa_num)) |>
  group_by(time_socical_media) |>
  summarise(
    mean_gpa = mean(gpa_num),
    se = sd(gpa_num) / sqrt(n()),
    .groups = "drop"
  ) |>
  ggplot(aes(x = time_socical_media, y = mean_gpa, group = 1)) +
  geom_line() +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin = mean_gpa - 1.96 * se, ymax = mean_gpa + 1.96 * se), width = 0.1) +
  scale_y_continuous(breaks = 1:5) +
  labs(x = NULL, y = "Mean GPA category (1=Poor … 5=Excellent)",
       title = "GPA trend by time spent on social media") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1))
```
:::

# 4.Overall Summary of Findings

Across the seven observations, several consistent patterns emerged regarding students’ academic performance and their perceived learning environment. First, GPA distribution appears moderately concentrated in the middle-to-upper categories, suggesting that the majority of students perceive their academic standing as satisfactory or above average.

Second, institutional factors such as lecturer quality, curriculum suitability, and university facilities demonstrate noticeable variation in student evaluations. While overall ratings tend toward the positive range, dispersion patterns indicate that certain subgroups experience the learning environment differently.

Third, perceived academic adaptation, study methods, and institutional support show meaningful associations with GPA levels. Students reporting stronger adaptation and more effective study strategies generally fall within higher GPA categories. In contrast, time allocation variables reveal mixed relationships, indicating that academic performance is influenced not only by effort quantity but also by perceived learning quality and support structures.

Finally, peer influence and competitive classroom environments appear to shape students’ academic experience, though their impact seems more contextual than deterministic.

Collectively, these findings suggest that academic performance is not driven by a single variable but rather by a combination of individual learning behaviors and institutional support mechanisms.

# 5.Key Takeaways and Implications

-    Improving teaching quality and curriculum alignment may indirectly enhance student performance, as institutional perception is closely linked with academic outcomes.

-    Academic adaptation and study strategies should be prioritized in student support programs, as they demonstrate stronger association with higher GPA levels than time investment alone.

-    Targeted academic interventions may be more effective than universal policies, especially for students reporting weaker adaptation or lower institutional support.

-    Learning environment improvements (facilities, lecturer engagement, structured support) could produce long-term benefits, beyond short-term grade improvements.

-    Balanced peer environments that encourage collaboration rather than excessive competition may foster healthier academic development.

-    Sustainable academic success likely requires coordinated efforts at both the individual and institutional levels.

# 6.Limitations

-   The analysis is based on self-reported survey data, which may be subject to response bias and social desirability effects.

<!-- -->

-    The cross-sectional design limits the ability to infer causal relationships between academic performance and perceived institutional factors.

<!-- -->

-    Likert-scale responses are treated as ordinal measures, which may constrain the interpretation of mean-based comparisons.

<!-- -->

-    The dataset reflects perceptions within a specific institutional context, potentially limiting generalizability to other universities or student populations.

<!-- -->

-    Some relationships observed may be influenced by unmeasured confounding variables (e.g., prior academic ability or socioeconomic background).
